---
title: "Cabbages"
author: "Logan Kimbrough"
date: "Sept 2020"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

The difference in between c39 and c52 is that c52 has a greater capacity of VitaminC.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

The graphical method to give us results is to grab the data from c39 and c52 to form it into the boxplot. The numercial method is to have the data and to find the mean, max, median, min and put it into a chart format where you are able to read it by number rather than the graph.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

The results upon the descriptive results show that c39 have less VitaminC than c52.

The results upon the inferential results show that the the odds of something like this happening is a very minuscule chance.

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(VitC~Cult,data=veggy)
```
  
According to the boxplot the graphical results show that c52 looks bigger than c39.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
  
The mean amount of c39 is 51.5 and the mean amount for c52 is 64.4. The difference in between both is around 13 therefore the mean for c52 is larger.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
  
The chances of getting these results is .00000003405 if the null hypothesis is true. So I doubt the null hypothesis is true. I reject the null hypothesis. The c52 appears to have more vitaminC than the c39.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The challenge value is 5%, it is much smaller than .05 therefore the odds of getting something like this happens .00000003405 of the time.
